---
title: "Combine Data for Combustion Model"
author: "Anna Talucci"
date: "2023-08-03"
output: html_document
---


# Overview
 For 20 landscapes clean and combine data for combustion model.
 
 Create on data frame with all sampled points and variables. The dataframe will be subset in the model script.

# Librarys
```{r}
library(tidyverse)
```

# Data

## FWI

```{r}
fwi <- list.files(path="../data/LandscapeData/fwi",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  bind_rows() %>%
  dplyr::select(BUI:FWI, ID1, ID2, ISI, rh:wspeed) %>%
  rename(DOB_lst=DOB_Ist, Relative.humidity=rh, Temperature=t, Wind.speed=wspeed,VPD = vpd,) 
```

```{r}
fwi 
```

```{r}
min(fwi$FWI)
max(fwi$FWI)
```

```{r}
fwiBurnDate <- list.files(path="../data/LandscapeData/fwiBurnDate",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  bind_rows() %>%
  dplyr::select(BUI:FWI, ID1, ID2, ISI, rh:wspeed) %>%
  rename(DOB_lst=DOB_Ist, Relative.humidity=rh, Temperature=t, Wind.speed=wspeed,VPD = vpd,) 
```

```{r}
fwiBurnDate
```

```{r}
min(fwiBurnDate$FWI)
max(fwiBurnDate$FWI)
```
## Landsat
### Veg
```{r}
veg =  list.files(path="../data/LandscapeData/LandsatVeg",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows() %>%
  dplyr::select(ID:rdnbr) %>%
  rename(NDVI=dNDVI, NDII=dNDII)
```
```{r}
veg
```

### TCT
```{r}
tct =  list.files(path="../data/LandscapeData/landsatTCT",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows() %>% 
  dplyr::select(ID1:ID2, brightness, fireID:greenness, wetness)
```

```{r}
tct
```

### Tree Cover
```{r}
treecover =  list.files(path="../data/LandscapeData/treeCover",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows() %>%
  dplyr::select(ID1, ID2, fireID, tree_canopy_cover) %>%
  rename(Tree.cover=tree_canopy_cover) 
```

```{r}
treecover 
```
###Join
```{r}
( landsat = full_join(veg, tct, by = c("ID1", "ID2", "fireID")) %>%
    full_join(., treecover, by = c("ID1", "ID2", "fireID")))
```
## Static
### Terrain
```{r}
terrain =  list.files(path="../data/LandscapeData/staticTerrain",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows() %>%
  dplyr::select(ID:slope)
```

```{r}
terrain 
```

### veg
```{r}
sveg =  list.files(path="../data/LandscapeData/staticVeg",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows() %>%
  dplyr::select(BS:GRSH, ID1:OCON, WS, fireID)
```

```{r}
sveg 
```

### Soil
```{r}
ssoil =  list.files(path="../data/LandscapeData/staticSoil",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows()  %>%
  dplyr::select(BD_30, Clay_30, ID1, ID2, SOC_30:Silt_30, pH_30, fireID)  
```

```{r}
ssoil
```

### Soil
```{r}
spfi =  list.files(path="../data/LandscapeData/staticPFI",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows()  %>%
  dplyr::select(ID1, ID2, PFI, fireID)
```

```{r}
spfi
```

### Join
```{r}
( static = full_join(terrain, sveg, by = c("ID1", "ID2", "fireID")) %>%
    full_join(., ssoil, by = c("ID1", "ID2", "fireID")) %>%
    full_join(., spfi, by = c("ID1", "ID2", "fireID")) )
```







## Climate NA

```{r}
climateNA =  list.files(path="../data/LandscapeData/climateNA",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  bind_rows() %>%
  dplyr::select(id1, id2, AHM, CMD, CMD_sm, DD_0, DD_18, DD5, DD5_sm, EMT, Eref, Eref_sm, EXT, MAP, PAS, Rad_sm, SHM, Tmax_sm, Tmin_sm) %>%
  rename(ID1=id1, ID2=id2, CNA_AHM=AHM, CNA_CMD=CMD, CNA_CMD_5_8 = CMD_sm, CNA_DD_0=DD_0, CNA_DD_18=DD_18, CNA_DD5=DD5, CNA_DD5_5_8=DD5_sm, CNA_EMT=EMT, CNA_Eref=Eref, CNA_Eref_5_8=Eref_sm, CNA_EXT=EXT, CNA_MAP=MAP, CNA_PAS=PAS, CNA_Rad_5_8=Rad_sm, CNA_SHM=SHM, CNA_Tmax_5_8=Tmax_sm, CNA_Tmin_5_8=Tmin_sm) 
  
```

```{r}
climateNA 
```

# Check number of IDs
```{r}
length(unique(landsat$ID1))
length(unique(static$ID1))
length(unique(fwi$ID1))
length(unique(fwiBurnDate$ID1))
length(unique(climateNA$ID1))
```
fwiBurnDate
```{r}
length(unique(landsat$ID2))
length(unique(static$ID2))
length(unique(fwi$ID2))
length(unique(fwiBurnDate$ID2))
length(unique(climateNA$ID2))
```



# Combine to Datasets
tibble::rowid_to_column(data, "ID")
full_join(terrain, sveg, by = c("ID1", "ID2", "fireID")) )
```{r}
allData = full_join(static, landsat, by = c("ID1", "ID2", "ID", "eco", "RID", "fireID", "lat", "lon")) %>%
  full_join(., climateNA, by = c("ID1", "ID2")) %>%
  full_join(., fwi, by = c("ID1", "ID2")) 
```

```{r}
allData
```

```{r}
allDataBurnDate = full_join(static, landsat, by = c("ID1", "ID2", "ID", "eco", "RID", "fireID", "lat", "lon")) %>%
  full_join(., climateNA, by = c("ID1", "ID2")) %>%
  full_join(., fwiBurnDate, by = c("ID1", "ID2")) 
```

```{r}
allDataBurnDate
```

## Check NAs
There are several NAs for the FWI Data

```{r}
allData[rowSums(is.na(allData)) > 0,]
```

```{r}
naData = allData[rowSums(is.na(allData)) > 0,]
```

```{r}
unique(naData$ID)
```
```{r}
naFree = allData %>% drop_na(FWI)
```

```{r}
naFree %>% group_by(ID, ID2) %>% summarize(ct = n())
```


# Write to csv

```{r}
write_csv(allData, "../outputs/Landscape20DataCombustionModel.csv")
```

```{r}
write_csv(allDataBurnDate, "../outputs/L20DataBurnDateCombustionModel.csv")
```
**THE END**