---
title: "Combine Data for Combustion Model"
author: "Anna Talucci"
date: "2023-08-03"
output: html_document
---


# Overview
 For 20 landscapes clean and combine data for combustion model.

# Librarys
```{r}
library(tidyverse)
```

# Data

## FWI
## List of rasters
```{r}
fwi <- list.files(path="../data/LandscapeData/fwi",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  bind_rows() %>%
  dplyr::select(BUI:wspeed) %>%
  rename(DOB_lst=DOB_Ist, Relative.humidity=rh, Temperature=t, Wind.speed=wspeed,VPD = vpd,) 
```

```{r}
fwi 
```

## Landsat
### Veg
```{r}
veg =  list.files(path="../data/LandscapeData/LandsatVeg",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows() %>%
  dplyr::select(ID:rdnbr)
```
```{r}
veg
```

### TCT
```{r}
tct =  list.files(path="../data/LandscapeData/landsatTCT",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows() %>% 
  dplyr::select(ID1:ID2, brightness, fireID:greenness, wetness)
```

```{r}
tct
```

## Tree Cover
```{r}
treecover =  list.files(path="../data/LandscapeData/treeCover",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows() %>%
  dplyr::select(ID1, ID2, fireID, tree_canopy_cover) %>%
  rename(Tree.cover=tree_canopy_cover) 
```

```{r}
treecover 
```

```{r}
( landsat = full_join(veg, tct, by = c("ID1", "ID2", "fireID")) %>%
    full_join(., treecover, by = c("ID1", "ID2", "fireID")))
```
## Static
### Terrain
```{r}
terrain =  list.files(path="../data/LandscapeData/staticTerrain",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows() %>%
  dplyr::select(ID:start)
```

```{r}
terrain 
```

### veg
```{r}
sveg =  list.files(path="../data/LandscapeData/staticVeg",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows() %>%
  dplyr::select(BS:GRSH, ID1:OCON, WS, fireID)
```

```{r}
sveg 
```

```{r}
( static = full_join(terrain, sveg, by = c("ID1", "ID2", "fireID")) )
```




## Climate NA

```{r}
climateNA =  list.files(path="../data/LandscapeData/climateNA",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  bind_rows() %>%
  dplyr::select(id1:Elevation, AHM, CMD, CMD_sm, DD_0, DD_18, DD5, DD5_sm, EMT, Eref, Eref_sm, EXT, MAP, PAS, Rad_sm, SHM, Tmax_sm, Tmin_sm) %>%
  rename(ID1=id1, ID2=id2, lat=Latitude, lon=Longitude, elevation = Elevation, CNA_AHM=AHM, CNA_CMD=CMD, CNA_CMD_5_8 = CMD_sm, CNA_DD_0=DD_0, CNA_DD_18=DD_18, CNA_DD5=DD5, CNA_DD5_5_8=DD5_sm, CNA_EMT=EMT, CNA_Eref=Eref, CNA_Eref_5_8=Eref_sm, CNA_EXT=EXT, CNA_MAP=MAP, CNA_PAS=PAS, CNA_Rad_5_8=Rad_sm, CNA_SHM=SHM, CNA_Tmax_5_8=Tmax_sm, CNA_Tmin_5_8=Tmin_sm)
```

```{r}
climateNA 
```




CNA_AHM, CNA_CMD, CNA_CMD_5_8, CNA_DD_0, CNA_DD_18, CNA_DD5, CNA_DD5_5_8, CNA_EMT, CNA_Eref, CNA_Eref_5_8, CNA_EXT, CNA_MAP, CNA_PAS, CNA_Rad_5_8, CNA_SHM, CNA_Tmax_5_8, CNA_Tmin_5_8,








# Check number of IDs
```{r}
length(unique(landsat$ID1))
length(unique(static$ID1))
length(unique(fwi$ID1))
length(unique(climateNA$ID1))
```

```{r}
length(unique(landsat$ID2))
length(unique(static$ID2))
length(unique(fwi$ID2))
length(unique(climateNA$ID2))
```



# Combine to Datasets
tibble::rowid_to_column(data, "ID")
full_join(terrain, sveg, by = c("ID1", "ID2", "fireID")) )
```{r}
static_landsat = full_join(static, landsat, by = c("ID1", "ID2", "fireID", "lat", "lon")) 

static_landsat
```

```{r}
static_landsat_fwi = full_join(static_landsat, fwi1, by = c("ID1", "ID2", "fireID", "lat", "lon")) 

static_landsat_fwi
```


```{r}
df_for_cna1 = tibble::rowid_to_column(static_landsat_fwi, "ID") %>% 
  rename(ID1 = ID, UniqueID = ID1) 

df_for_cna2 = df_for_cna1 %>% 
  dplyr::select(ID1, ID2, lat, lon, elevation)
```


# Select only data of interest to predict
## For above
```{r}
model_data = static_landsat_fwi_cna %>% 
  rename(DOB_lst=DOB_Ist, Relative.humidity=rh, Temperature=t, Tree.cover=tree_canopy_cover, Wind.speed=wspeed,VPD = vpd, burn_year=ID2.x, lat= lat.x, lon=lon.x) %>%
  dplyr::select(-ID2.y,-lat.y, -lon.y )

model_data

```

```{r}
write_csv(model_data, "../outputs/Landscape1DataForCombustionModel.csv")
```
%>%
  dplyr::select(ID1, ID2, NAME, FIREID, UniqueID, lat, lon, BD_30, brightness, BS, BUI, Clay_30, CNA_AHM, CNA_CMD, CNA_CMD_5_8, CNA_DD_0, CNA_DD_18, CNA_DD5, CNA_DD5_5_8, CNA_EMT, CNA_Eref, CNA_Eref_5_8, CNA_EXT, CNA_MAP, CNA_PAS, CNA_Rad_5_8, CNA_SHM, CNA_Tmin_5_8, DC, DEC, DMC, dNBR, DOB_lst, elevation, FFMC, greenness, JP, NDII, NDVI, NV, PFI, pH_30, rbr, rdnbr, Relative.humidity, Ruggedness, Sand_30, Silt_30, slope, SOC_30, Temperature, Tree.cover, wetness, Wind.speed, WS)
## For Below
```{r}
below = static_landsat_fwi_cna %>% 
  rename(DOB_lst=DOB_Ist, Relative.humidity=rh, Temperature=t, Tree.cover=tree_canopy_cover, Wind.speed=wspeed, ID2=ID2.x, lat= lat.x, lon=lon.x) 


below
```
%>%
  dplyr::select(ID1, ID2, NAME, FIREID, UniqueID, lat, lon, BD_30, brightness, BS, BUI, Clay_30, CNA_AHM, CNA_CMD, CNA_CMD_5_8, CNA_DD_0, CNA_DD_18, CNA_DD5, CNA_DD5_5_8, CNA_EMT, CNA_Eref, CNA_Eref_5_8, CNA_EXT, CNA_MAP, CNA_PAS, CNA_Rad_5_8, CNA_SHM, CNA_Tmax_5_8, CNA_Tmin_5_8, DC, DEC, DMC, dNBR, DOB_lst, elevation, FFMC, greenness, JP, NDII, NDVI, NV, PFI, pH_30, rbr, rdnbr, Relative.humidity, Ruggedness, Sand_30, Silt_30, slope, SOC_30, Tree.cover, wetness, Wind.speed, WS)

# Write to csv
```{r}
write_csv(above, "../outputs/Landscape1DataForCombustionModelABOVE.csv")
```
```{r}
write_csv(below, "../outputs/Landscape1DataForCombustionModelBELOW.csv")
```

```{r}
write_csv(static_landsat_fwi_cna, "../outputs/Landscape1DataForCombustionModel.csv")
```
**THE END**