---
title: "Combine Data for Combustion Model"
author: "Anna Talucci"
date: "2023-08-03"
output: html_document
---


# Overview
 For 20 landscapes clean and combine data for combustion model.

# Librarys
```{r}
library(tidyverse)
```

# Data

## FWI
## List of rasters
```{r}
fwi <- list.files(path="../data/LandscapeData/fwi",pattern='*.csv', full.names = TRUE) %>% purrr::map(., read_csv) %>% bind_rows ()
```

```{r}
fwi 
```

## Landsat
### Veg
```{r}
veg =  list.files(path="../data/LandscapeData/LandsatVeg",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows ()
```
```{r}
veg
```

### TCT
```{r}
tct =  list.files(path="../data/LandscapeData/landsatTCT",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows ()
```

```{r}
tct
```



## Static
### Terrain
```{r}
terrain =  list.files(path="../data/LandscapeData/staticTerrain",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows ()
```

```{r}
terrain 
```

### veg
```{r}
sveg =  list.files(path="../data/LandscapeData/staticVeg",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows ()
```

```{r}
sveg 
```

## Tree Cover
```{r}
treecover =  list.files(path="../data/LandscapeData/treeCover",pattern='*.csv', full.names = TRUE) %>% 
  purrr::map(., read_csv) %>% 
  map_dfr(., ~ .x %>%
        mutate(across(fireID, as.character))) %>%
  bind_rows ()
```

```{r}
treecover 
```


## Climate NA

## DELETE!!?!?!?!??!
```{r}
static =  read.csv("../data/Landscape1/Static/static_test.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

```{r}
terrain =  read.csv("../data/Landscape1/Static/Static_terrain.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

```{r}
veg =  read.csv("../data/Landscape1/Static/static_vegetation_3338.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

```{r}
static
```

```{r}
veg
```

```{r}
terrain
```


## Climate NA
```{r}
cna =  read.csv("../data/Landscape1/CNA/Landscape1CLimateNAData2.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

```{r}
head(cna)
```

# Select columns 
## Static
```{r}
terrain_veg = full_join(terrain, veg, by = c("ID1", "ID2", "FIREID", "NAME", "lat", "lon")) %>%
  dplyr::select(-system.index.x, -.geo.x, -system.index.y, -.geo.y)
```

```{r}
static
```
```{r}
static1 = static %>% 
  dplyr::select(-system.index, -Ruggedness, -key, -.geo) 
```

```{r}
static2 = full_join(static1, terrain_veg, by = c("ID1", "ID2", "FIREID", "NAME", "lat", "lon")) 

static2
```

## landsat
```{r}
landsat1 = landsat %>% 
  dplyr::select(FIREID:wetness) 

landsat1
```

```{r}
landsat %>%
  dplyr::select(ID1, ID2, lat, lon) %>%
  write_csv(., "../outputs/ID1ID2LatLon.csv")
```
## FWI
```{r}
fwi1 = fwi_bind %>% 
  dplyr::select(BUI:wspeed)  
```

```{r}
fwi1 %>% dplyr::select(ID1, ID2, lat, lon) %>% write_csv(., "../outputs/Landscape1ForCNAFromFWI.csv")
```




# Check number of IDs
```{r}
length(unique(landsat1$ID1))
length(unique(static2$ID1))
length(unique(fwi1$ID1))
length(unique(cna$ID1))
```

```{r}
length(unique(landsat1$ID2))
length(unique(static2$ID2))
length(unique(fwi1$ID2))
length(unique(cna$ID2))
```
# head
```{r}
fwi1
```

# Combine to figure out join issue with CNA
tibble::rowid_to_column(data, "ID")
```{r}
static_landsat = full_join(static2, landsat1, by = c("ID1", "ID2", "FIREID", "NAME", "lat", "lon")) 

static_landsat
```

```{r}
static_landsat_fwi = full_join(static_landsat, fwi1, by = c("ID1", "ID2", "FIREID", "NAME", "lat", "lon")) 

static_landsat_fwi
```


```{r}
df_for_cna1 = tibble::rowid_to_column(static_landsat_fwi, "ID") %>% 
  rename(ID1 = ID, UniqueID = ID1) 

df_for_cna2 = df_for_cna1 %>% 
  dplyr::select(ID1, ID2, lat, lon, elevation)
```

# Write to csv
```{r eval=FALSE, include=FALSE}
write_csv(df_for_cna, "../outputs/Landscape1DFforCNA.csv")
```

# Add CNA

```{r}
static_landsat_fwi_cna = full_join(df_for_cna1, cna, by = c("ID1")) 

static_landsat_fwi_cna
```

```{r}
static_landsat_fwi_cna
```
# Select only data of interest to predict
## For above
```{r}
model_data = static_landsat_fwi_cna %>% 
  rename(DOB_lst=DOB_Ist, Relative.humidity=rh, Temperature=t, Tree.cover=tree_canopy_cover, Wind.speed=wspeed,VPD = vpd, burn_year=ID2.x, lat= lat.x, lon=lon.x) %>%
  dplyr::select(-ID2.y,-lat.y, -lon.y )

model_data

```

```{r}
write_csv(model_data, "../outputs/Landscape1DataForCombustionModel.csv")
```
%>%
  dplyr::select(ID1, ID2, NAME, FIREID, UniqueID, lat, lon, BD_30, brightness, BS, BUI, Clay_30, CNA_AHM, CNA_CMD, CNA_CMD_5_8, CNA_DD_0, CNA_DD_18, CNA_DD5, CNA_DD5_5_8, CNA_EMT, CNA_Eref, CNA_Eref_5_8, CNA_EXT, CNA_MAP, CNA_PAS, CNA_Rad_5_8, CNA_SHM, CNA_Tmin_5_8, DC, DEC, DMC, dNBR, DOB_lst, elevation, FFMC, greenness, JP, NDII, NDVI, NV, PFI, pH_30, rbr, rdnbr, Relative.humidity, Ruggedness, Sand_30, Silt_30, slope, SOC_30, Temperature, Tree.cover, wetness, Wind.speed, WS)
## For Below
```{r}
below = static_landsat_fwi_cna %>% 
  rename(DOB_lst=DOB_Ist, Relative.humidity=rh, Temperature=t, Tree.cover=tree_canopy_cover, Wind.speed=wspeed, ID2=ID2.x, lat= lat.x, lon=lon.x) 


below
```
%>%
  dplyr::select(ID1, ID2, NAME, FIREID, UniqueID, lat, lon, BD_30, brightness, BS, BUI, Clay_30, CNA_AHM, CNA_CMD, CNA_CMD_5_8, CNA_DD_0, CNA_DD_18, CNA_DD5, CNA_DD5_5_8, CNA_EMT, CNA_Eref, CNA_Eref_5_8, CNA_EXT, CNA_MAP, CNA_PAS, CNA_Rad_5_8, CNA_SHM, CNA_Tmax_5_8, CNA_Tmin_5_8, DC, DEC, DMC, dNBR, DOB_lst, elevation, FFMC, greenness, JP, NDII, NDVI, NV, PFI, pH_30, rbr, rdnbr, Relative.humidity, Ruggedness, Sand_30, Silt_30, slope, SOC_30, Tree.cover, wetness, Wind.speed, WS)

# Write to csv
```{r}
write_csv(above, "../outputs/Landscape1DataForCombustionModelABOVE.csv")
```
```{r}
write_csv(below, "../outputs/Landscape1DataForCombustionModelBELOW.csv")
```

```{r}
write_csv(static_landsat_fwi_cna, "../outputs/Landscape1DataForCombustionModel.csv")
```
**THE END**