---
title: "Landscape 1 combustion layer"
author: "Anna Talucci"
date: "2023-04-21"
output: html_document
---





# Overview

This script generates a point file from a  Landsat raster and fire perimeters to be used to extract WNA Climate data and then process combustion with ABoVE-FED.

# Packages
```{r}
library(terra)
library(gdalUtilities)
library(sf)
library(tidyverse)
```

# Data

## Shapefiles
```{r}
L1 = st_read("../data/FirstLandscape/caribou_pker_ck.shp", "caribou_pker_ck")
```
```{r}
st_crs(L1)$proj4string
L1_projection = st_crs(L1)$proj4string
st_crs(L1)$epsg
```

```{r}
fp1 = st_read("../data/Landscape1Perimeters/193__Boundary_20040901_1400/193__Boundary_20040901_1400.shp", "193__Boundary_20040901_1400")
fp2 = st_read("../data/Landscape1Perimeters/315_2016_Washington_Creek_20160706_1600/315_2016_Washington_Creek_20160706_1600.shp", "315_2016_Washington_Creek_20160706_1600")
fp3 = st_read("../data/Landscape1Perimeters/333_Poker_Creek_20160629_1600/333_Poker_Creek_20160629_1600.shp", "333_Poker_Creek_20160629_1600")
fp4 = st_read("../data/Landscape1Perimeters/538_Ruby_Creek_20150922_1400/538_Ruby_Creek_20150922_1400.shp", "538_Ruby_Creek_20150922_1400")
fp5 = st_read("../data/Landscape1Perimeters/352_Lost_Horse_Creek_20050703_1800/352_Lost_Horse_Creek_20050703_1800.shp", "352_Lost_Horse_Creek_20050703_1800")
```
```{r}
fp1
```

```{r}
st_crs(fp1)$proj4string
fp1_projection = st_crs(fp1)$proj4string
st_crs(fp1)$epsg
```
## Raster

```{r}
r1<-rast("../data/LandscapeRaster/FiSL-Landscape1.tif")
```


# Projections
```{r eval=FALSE, include=FALSE}
raster_proj = crs(r1)
```

# Reprojection
```{r eval=FALSE, include=FALSE}
reproj_r1 = terra::project(r1, L1_projection)
```

```{r eval=FALSE, include=FALSE}
l1_rasterproj = st_transform(L1, crs = raster_proj)
```

# Plot
```{r}
ggplot() + 
  geom_sf(data = L1, color = "blue") +
  geom_sf(data = fp1) +
  geom_sf(data = fp2) +
  geom_sf(data = fp3) +
  geom_sf(data = fp4) +
  geom_sf(data = fp5) +
  ggtitle("Landscape 1") + 
  coord_sf()
```
```{r}
fp1L1<-st_crop( fp1$geometry, L1$geometry)
fp5L1<-st_crop( fp5$geometry, L1$geometry)
```

```{r}
ggplot() + 
  geom_sf(data = fp1L1, color = "blue") +
  coord_sf()
```
```{r}
ggplot() + 
  geom_sf(data = L1, color = "blue") +
  geom_sf(data = fp1L1) +
  geom_sf(data = fp2) +
  geom_sf(data = fp3) +
  geom_sf(data = fp4) +
  geom_sf(data = fp5L1) +
  ggtitle("Landscape 1") + 
  coord_sf()
```
```{r}
intersect<-st_intersection( fp1$geometry, L1$geometry)

```

```{r}
ggplot() + 
  geom_sf(data = intersect, color = "blue") +
  coord_sf()
```


# For cropped polgygons in Landscape 1
 adding attributes back after cropping
 
## First create Dataframe of attributes
```{r}
fp1_df <- fp1 %>% st_drop_geometry()
fp5_df <- fp5 %>% st_drop_geometry()
```

```{r}
fp1_df
fp5_df
```

## Add attritue table


```{r}
fp1
```

## Add column names and fill NA
```{r}
fp1 = st_as_sf (fp1)
fp1L1 = st_as_sf (fp1L1)
join = st_join(fp1L1, fp1, join = st_covers)
fp1L1_v1 = join %>% 
  dplyr::select(NAME, FIREID, FIREYEAR) %>%
  mutate_at(vars(NAME), ~replace_na(., "Boundary")) %>%
  mutate_at(vars(FIREID), ~replace_na(., 1679)) %>%
  mutate_at(vars(FIREYEAR), ~replace_na(., "2004")) 
```
```{r}
fp5
```

```{r}
fp5 = st_as_sf (fp5)
fp5L1 = st_as_sf (fp5L1)
join5 = st_join(fp5L1, fp5, join = st_covers)
fp5L1_v1 = join5 %>% 
  dplyr::select(NAME, FIREID, FIREYEAR) %>%
  mutate_at(vars(NAME), ~replace_na(., "Lost Horse Creek")) %>%
  mutate_at(vars(FIREID), ~replace_na(., 2710)) %>%
  mutate_at(vars(FIREYEAR), ~replace_na(., "2005")) 

fp5L1_v1 
```
```{r}
ggplot() + 
  geom_sf(data = join, color = "blue") +
  coord_sf()
```

# Select attributes of interest for other fires
```{r}
fp2L1 = fp2 %>% dplyr::select(NAME, FIREID, FIREYEAR) 
fp2L1

fp3L1 = fp3 %>% dplyr::select(NAME, FIREID, FIREYEAR)
fp4L1 = fp4 %>% dplyr::select(NAME, FIREID, FIREYEAR) 
```

# Combine fires

```{r}
all_fires = dplyr::bind_rows(fp1L1_v1, fp2L1, fp3L1, fp4L1, fp5L1_v1)
all_fires

```

```{r}
st_write(all_fires, "../outputs/Landscape1Fires.shp", driver="ESRI Shapefile")
```

# Raster to points
```{r}
l1points = as.points(r1, values=TRUE, na.rm=TRUE)
```

```{r}
l1pts = st_as_sf(l1points)
```

```{r}
l1pts
```
# Write points to file

```{r eval=FALSE, include=FALSE}
st_write(l1pts, "../outputs/Landscape1_points.shp", driver="ESRI Shapefile")
```

# Plotting ...
```{r}
ggplot() + 
  
  geom_sf(data = l1pts, size=1.5, shape = 1, color ="grey50") +
  geom_sf(data = L1, color = "blue", fill=NA) +
  ggtitle("Raster points") + 
  coord_sf()
```

# Select only burned points
```{r}
burned = st_join(l1pts, all_fires) %>% drop_na(.)
```

```{r}
burned
```
```{r}
ggplot() + 
  geom_sf(data = burned, size=.5, shape = 1, color ="grey50") +
  geom_sf(data = L1, color = "blue", fill=NA) +
  geom_sf(data=all_fires, color = "red", fill=NA)
  ggtitle("Landscape 1") + 
  coord_sf()
```

# Write burned points to file
```{r eval=FALSE, include=FALSE}
st_write(burned, "../outputs/Landscape1_burned_points.shp", driver="ESRI Shapefile")
```