---
title: "Predict to Raster"
author: "Anna Talucci"
date: "2023-08-07"
output: html_document
---

# Overview
Combustion outputs predicted to raster
# Projections


# Packages
```{r}
library(terra)
library(gdalUtilities)
library(sf)
library(tidyverse)
library(stars)
```

# Data

## predictions

```{r}
above = read.csv("../data/PredictLandscapes/BurnDateAbovegroundCombustion.csv")
```


```{r}
below = read.csv("../data/PredictLandscapes/BurnDateBelowgroundCombustion.csv")
```

## landscapes

Shapefile for 20 landscapes of interest.
```{r}
L20 = st_read("../data/Landscapes/final_plots_lat_lon.shp", "final_plots_lat_lon")
```

```{r}
head(L20)
```

## Shapefiles
```{r}
pts = st_read("../data/burnPts/FislBurnPtsAllWgs.shp", "FislBurnPtsAllWgs")
```

```{r}
r1249 = rast("../data/LandsatRaster/wgs84/BI/Fisl_BI1249.tif")
r1800 = rast("../data/LandsatRaster/wgs84/BI/Fisl_BI1800.tif")
r1889 = rast("../data/LandsatRaster/wgs84/BI/Fisl_BI1889.tif")
r1891 = rast("../data/LandsatRaster/wgs84/BI/Fisl_BI1891.tif")
r1982 = rast("../data/LandsatRaster/wgs84/BI/Fisl_BI1982.tif")
```

```{r}
r3952 = rast("../data/LandsatRaster/wgs84/BC/Fisl_BC3952.tif")
r4049 = rast("../data/LandsatRaster/wgs84/BC/Fisl_BC4049.tif")
r4139 = rast("../data/LandsatRaster/wgs84/BC/Fisl_BC4139.tif")
r4219 = rast("../data/LandsatRaster/wgs84/BC/Fisl_BC4219.tif")
r4220 = rast("../data/LandsatRaster/wgs84/BC/Fisl_BC4220.tif")
```

```{r}
r5938 = rast("../data/LandsatRaster/wgs84/TP/Fisl_TP5938.tif")
r5939 = rast("../data/LandsatRaster/wgs84/TP/Fisl_TP5939.tif")
r6393 = rast("../data/LandsatRaster/wgs84/TP/Fisl_TP6393.tif")
r6755 = rast("../data/LandsatRaster/wgs84/TP/Fisl_TP6755.tif")
```

```{r}
r8301 = rast("../data/LandsatRaster/wgs84/TS/Fisl_TS8301.tif")
r8392 = rast("../data/LandsatRaster/wgs84/TS/Fisl_TS8392.tif")
r8937 = rast("../data/LandsatRaster/wgs84/TS/Fisl_TS8937.tif")
```


## List of rasters


```{r}
bilist <- list.files(path="../data/LandsatRaster/wgs84/BI",pattern='tif$', full.names = TRUE)
bclist <- list.files(path="../data/LandsatRaster/wgs84/BC",pattern='tif$', full.names = TRUE)
tplist <- list.files(path="../data/LandsatRaster/wgs84/TP",pattern='tif$', full.names = TRUE)
tslist <- list.files(path="../data/LandsatRaster/wgs84/TS",pattern='tif$', full.names = TRUE)
```

### Name items in a list with file name
```{r}
names(bilist) <- tools::file_path_sans_ext(basename(bilist))
names(bclist) <- tools::file_path_sans_ext(basename(bclist))
names(tplist) <- tools::file_path_sans_ext(basename(tplist))
names(tslist) <- tools::file_path_sans_ext(basename(tslist))
```

```{r}
rasters <- function(list){ 
  purrr::map(list, rast) 
}
```


```{r}
rbi = rasters(bilist)
rbc = rasters(bclist)
rtp = rasters(tplist)
rts = rasters(tslist)
```


# look at data

```{r}
head(pts)
```

```{r}
head(above)
```

```{r}
rbi
```
```{r}
rbc
```

```{r}
rtp
```
## raster

# Join Predic to Points


```{r}
above_pts = full_join(pts, above, by = c("ID1", "ID2", "ID", "eco", "fireID", "RID", "lat", "lon")) %>% drop_na()
```

```{r}
above_pts
```

```{r}
below_pts = full_join(pts, below, by = c("ID1", "ID2", "ID", "eco", "fireID", "RID", "lat", "lon")) %>% drop_na()
```

```{r}
below_pts
```

```{r}
above_pts %>% st_drop_geometry() %>% group_by(eco, ID, ID2) %>% summarize(n=n())


```
BI	2000		
BI	2002			
BI	2005		
BI	2009			
BI	2010		
BI	2013			
BI	2015			
BI	2016		
TP	2013			
TP	2015			
TS	2015	

# Check crs match
```{r}
st_crs(below_pts)$proj4string
crs(r, proj=TRUE)
```
```{r}
st_crs(below_pts) 
```

```{r}
project(rbi$FiSLBI1249, crs =4326)

```

# Filter points & Landscape
```{r}
sort(unique(above_pts$ID))
```

```{r}
above1249 = above_pts %>% filter(ID==1249)
above1891 = above_pts %>% filter(ID==1891)
above1800 = above_pts %>% filter(ID==1800)
above1889 = above_pts %>% filter(ID==1889)
above1982 = above_pts %>% filter(ID==1982)
```

```{r}
above3952 = above_pts %>% filter(ID==3952)
above4049 = above_pts %>% filter(ID==4049)
above4139 = above_pts %>% filter(ID==4139)
above4219 = above_pts %>% filter(ID==4219)
above4220 = above_pts %>% filter(ID==4220)
```

```{r}
above5938 = above_pts %>% filter(ID==5938)
above5939 = above_pts %>% filter(ID==5939)
above6393 = above_pts %>% filter(ID==6393)
above6755 = above_pts %>% filter(ID==6755)
```

```{r}
above8301 = above_pts %>% filter(ID==8301)
above8392 = above_pts %>% filter(ID==8392)
above8937 = above_pts %>% filter(ID==8937)
```

```{r}
unique(below_pts$ID)
```
## Below
```{r}
below1249 = below_pts %>% filter(ID==1249)
below1891 = below_pts %>% filter(ID==1891)
below1800 = below_pts %>% filter(ID==1800)
below1889 = below_pts %>% filter(ID==1889)
below1982 = below_pts %>% filter(ID==1982)
```

```{r}
below3952 = below_pts %>% filter(ID==3952)
below4049 = below_pts %>% filter(ID==4049)
below4139 = below_pts %>% filter(ID==4139)
below4219 = below_pts %>% filter(ID==4219)
below4220 = below_pts %>% filter(ID==4220)
```

```{r}
below5938 = below_pts %>% filter(ID==5938)
below5939 = below_pts %>% filter(ID==5939)
below6393 = below_pts %>% filter(ID==6393)
below6755 = below_pts %>% filter(ID==6755)
```

```{r}
below8301 = below_pts %>% filter(ID==8301)
below8392 = below_pts %>% filter(ID==8392)
below8937 = below_pts %>% filter(ID==8937)
```
## landscapes
```{r}
L1249 = L20 %>% filter(ID==1249)
L1891 = L20 %>% filter(ID==1891)
L1800 = L20 %>% filter(ID==1800)
L1889 = L20 %>% filter(ID==1889)
L1982 = L20 %>% filter(ID==1982)
```

```{r}
L3952 = L20 %>% filter(ID==3952)
L4049 = L20 %>% filter(ID==4049)
L4139 = L20 %>% filter(ID==4139)
L4219 = L20 %>% filter(ID==4219)
L4220 = L20 %>% filter(ID==4220)
```

```{r}
L5938 = L20 %>% filter(ID==5938)
L5939 = L20 %>% filter(ID==5939)
L6393 = L20 %>% filter(ID==6393)
L6755 = L20 %>% filter(ID==6755)
```

```{r}
L8301 = L20 %>% filter(ID==8301)
L8392 = L20 %>% filter(ID==8392)
L8937 = L20 %>% filter(ID==8937)
```

# Make Raster 

## Above
```{r}
r_above1249 =  rasterize(vect(above1249), r1249, field = "prediction")
r_above1891 =  rasterize(vect(above1891), r1891, field = "prediction")
r_above1800 =  rasterize(vect(above1800), r1800, field = "prediction")
r_above1889 =  rasterize(vect(above1889), r1889, field = "prediction")
r_above1982 =  rasterize(vect(above1982), r1982, field = "prediction")
```

```{r}
r_above3952 = rasterize(vect(above3952), r3952, field = "prediction")
r_above4049 = rasterize(vect(above4049), r4049, field = "prediction")
r_above4139 = rasterize(vect(above4139), r4139, field = "prediction")
r_above4219 = rasterize(vect(above4219), r4219, field = "prediction")
r_above4220 = rasterize(vect(above4220), r4220, field = "prediction")
```

```{r}
r_above5938 =  rasterize(vect(above5938), r5938, field = "prediction")
r_above5939 =  rasterize(vect(above5939), r5939, field = "prediction")
r_above6393 =  rasterize(vect(above6393), r6393, field = "prediction")
r_above6755 =  rasterize(vect(above6755), r6755, field = "prediction")
```

```{r}
r_above8301 = rasterize(vect(above8301), r8301, field = "prediction")
r_above8392 = rasterize(vect(above8392), r8392, field = "prediction")
r_above8937 = rasterize(vect(above8937), r8937, field = "prediction")
```


## Below
```{r}
r_below1249 =  rasterize(vect(below1249), r1249, field = "prediction")
r_below1891 =  rasterize(vect(below1891), r1891, field = "prediction")
r_below1800 =  rasterize(vect(below1800), r1800, field = "prediction")
r_below1889 =  rasterize(vect(below1889), r1889, field = "prediction")
r_below1982 =  rasterize(vect(below1982), r1982, field = "prediction")
```

```{r}
r_below3952 = rasterize(vect(below3952), r3952, field = "prediction")
r_below4049 = rasterize(vect(below4049), r4049, field = "prediction")
r_below4139 = rasterize(vect(below4139), r4139, field = "prediction")
r_below4219 = rasterize(vect(below4219), r4219, field = "prediction")
r_below4220 = rasterize(vect(below4220), r4220, field = "prediction")
```

```{r}
r_below5938 =  rasterize(vect(below5938), r5938, field = "prediction")
r_below5939 =  rasterize(vect(below5939), r5939, field = "prediction")
r_below6393 =  rasterize(vect(below6393), r6393, field = "prediction")
r_below6755 =  rasterize(vect(below6755), r6755, field = "prediction")
```

```{r}
r_below8301 = rasterize(vect(below8301), r8301, field = "prediction")
r_below8392 = rasterize(vect(below8392), r8392, field = "prediction")
r_below8937 = rasterize(vect(below8937), r8937, field = "prediction")
```


# Clip raster to landscape

## Above
```{r}
cropAbove1249 = mask(crop(r_above1249,L1249),L1249)
cropAbove1891 = mask(crop(r_above1891,L1891),L1891)
cropAbove1800 = mask(crop(r_above1800,L1800),L1800)
cropAbove1889 = mask(crop(r_above1889,L1889),L1889)
cropAbove1982 = mask(crop(r_above1982,L1982),L1982)
```

```{r}
cropAbove3952 = mask(crop(r_above3952,L3952),L3952)
cropAbove4049 = mask(crop(r_above4049,L4049),L4049)
cropAbove4139 = mask(crop(r_above4139,L4139),L4139)
cropAbove4219 = mask(crop(r_above4219,L4219),L4219)
cropAbove4220 = mask(crop(r_above4220,L4220),L4220)
```

```{r}
cropAbove5938 = mask(crop(r_above5938,L5938),L5938)
cropAbove5939 = mask(crop(r_above5939,L5939),L5939)
cropAbove6393 = mask(crop(r_above6393,L6393),L6393)
cropAbove6755 = mask(crop(r_above6755,L6755),L6755)
```

```{r}
cropAbove8301 = mask(crop(r_above8301,L8301),L8301)
cropAbove8392 = mask(crop(r_above8392,L8392),L8392)
cropAbove8937 = mask(crop(r_above8937,L8937),L8937)
```



## Below
```{r}
cropBelow1249 = mask(crop(r_below1249,L1249),L1249)
cropBelow1891 = mask(crop(r_below1891,L1891),L1891)
cropBelow1800 = mask(crop(r_below1800,L1800),L1800)
cropBelow1889 = mask(crop(r_below1889,L1889),L1889)
cropBelow1982 = mask(crop(r_below1982,L1982),L1982)
```

```{r}
cropBelow3952 = mask(crop(r_below3952,L3952),L3952)
cropBelow4049 = mask(crop(r_below4049,L4049),L4049)
cropBelow4139 = mask(crop(r_below4139,L4139),L4139)
cropBelow4219 = mask(crop(r_below4219,L4219),L4219)
cropBelow4220 = mask(crop(r_below4220,L4220),L4220)
```

```{r}
cropBelow5938 = mask(crop(r_below5938,L5938),L5938)
cropBelow5939 = mask(crop(r_below5939,L5939),L5939)
cropBelow6393 = mask(crop(r_below6393,L6393),L6393)
cropBelow6755 = mask(crop(r_below6755,L6755),L6755)
```

```{r}
cropBelow8301 = mask(crop(r_below8301,L8301),L8301)
cropBelow8392 = mask(crop(r_below8392,L8392),L8392)
cropBelow8937 = mask(crop(r_below8937,L8937),L8937)
```


# Stack rasters & name bands
```{r}
stk1249 = c(cropAbove1249, cropBelow1249)
stk1891 = c(cropAbove1891, cropBelow1891)
stk1800 = c(cropAbove1800, cropBelow1800)
stk1889 = c(cropAbove1889, cropBelow1889)
stk1982 = c(cropAbove1982, cropBelow1982)
```

```{r}
stk3952 = c(cropAbove3952, cropBelow3952)
stk4049 = c(cropAbove4049, cropBelow4049)
stk4139 = c(cropAbove4139, cropBelow4139)
stk4219 = c(cropAbove4219, cropBelow4219)
stk4220 = c(cropAbove4220, cropBelow4220)
```

```{r}
stk5938 = c(cropAbove5938, cropBelow5938)
stk5939 = c(cropAbove5939, cropBelow5939)
stk6393 = c(cropAbove6393, cropBelow6393)
stk6755 = c(cropAbove6755, cropBelow6755)
```

```{r}
stk8301 = c(cropAbove8301, cropBelow8301)
stk8392 = c(cropAbove8392, cropBelow8392)
stk8937 = c(cropAbove8937, cropBelow8937)
```

```{r}
names(stk1249) = c('above', 'below')
names(stk1891) = c('above', 'below')
names(stk1800) = c('above', 'below')
names(stk1889) = c('above', 'below')
names(stk1982) = c('above', 'below')
```

```{r}
names(stk3952) = c('above', 'below')
names(stk4049) = c('above', 'below')
names(stk4139) = c('above', 'below')
names(stk4219) = c('above', 'below')
names(stk4220) = c('above', 'below')
```

```{r}
names(stk5938) = c('above', 'below')
names(stk5939) = c('above', 'below')
names(stk6393) = c('above', 'below')
names(stk6755) = c('above', 'below')
```
```{r}
names(stk8301) = c('above', 'below')
names(stk8392) = c('above', 'below')
names(stk8937) = c('above', 'below')
```

# Check data
```{r}
stk8301
nlyr(stk8301)
names(stk8301)
```
```{r}
stk8392
nlyr(stk8392)
names(stk8392)
```

```{r}
stk8937
nlyr(stk8937)
names(stk8937)
```

```{r}
stk6755
nlyr(stk6755)
names(stk6755)
```

```{r}
stk4220
nlyr(stk4220)
names(stk4220)
```
# Plot
```{r}
stk5938 %>% 
  as.data.frame(xy = TRUE) %>%
ggplot() +
  geom_tile(aes(x = x, y = y, fill =  above)) +
    ggtitle("Aboveground combustion")

```

```{r}
stk5938 %>% 
  as.data.frame(xy = TRUE) %>%
ggplot() +
  geom_tile(aes(x = x, y = y, fill =  below)) +
  ggtitle("Belowground combustion")

```

# Write Rasters
```{r eval=FALSE, include=FALSE}
writeRaster(stk1249, "../outputs/LandscapeCombustion/CombustStack1249.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(stk1891, "../outputs/LandscapeCombustion/CombustStack1891.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(stk1800, "../outputs/LandscapeCombustion/CombustStack1800.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(stk1889, "../outputs/LandscapeCombustion/CombustStack1889.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(stk1982, "../outputs/LandscapeCombustion/CombustStack1982.tif", overwrite=TRUE, filetype="GTiff")
```

```{r eval=FALSE, include=FALSE}
writeRaster(stk3952, "../outputs/LandscapeCombustion/CombustStack3952.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(stk4049, "../outputs/LandscapeCombustion/CombustStack4049.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(stk4139, "../outputs/LandscapeCombustion/CombustStack4139.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(stk4219, "../outputs/LandscapeCombustion/CombustStack4219.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(stk4220, "../outputs/LandscapeCombustion/CombustStack4220.tif", overwrite=TRUE, filetype="GTiff")
```

```{r eval=FALSE, include=FALSE}
writeRaster(stk5938, "../outputs/LandscapeCombustion/CombustStack5938.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(stk5939, "../outputs/LandscapeCombustion/CombustStack5939.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(stk6393, "../outputs/LandscapeCombustion/CombustStack6393.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(stk6755, "../outputs/LandscapeCombustion/CombustStack6755.tif", overwrite=TRUE, filetype="GTiff")
```

```{r}
writeRaster(stk8301, "../outputs/LandscapeCombustion/CombustStack8301.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(stk8392, "../outputs/LandscapeCombustion/CombustStack8392.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(stk8937, "../outputs/LandscapeCombustion/CombustStack8937.tif", overwrite=TRUE, filetype="GTiff")
```

# Write Rasters
```{r eval=FALSE, include=FALSE}
writeRaster(cropAbove1249, "../outputs/LandscapeCombustion/aboveCombustion1249.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(cropAbove1891, "../outputs/LandscapeCombustion/aboveCombustion1891.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(cropAbove1800, "../outputs/LandscapeCombustion/aboveCombustion1800.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(cropAbove1889, "../outputs/LandscapeCombustion/aboveCombustion1889.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(cropAbove5938, "../outputs/LandscapeCombustion/aboveCombustion5938.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(cropAbove6393, "../outputs/LandscapeCombustion/aboveCombustion6393.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(cropAbove8301, "../outputs/LandscapeCombustion/aboveCombustion8301.tif", overwrite=TRUE, filetype="GTiff")
```

```{r eval=FALSE, include=FALSE}
writeRaster(cropBelow1249, "../outputs/LandscapeCombustion/belowCombustion1249.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(cropBelow1891, "../outputs/LandscapeCombustion/belowCombustion1891.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(cropBelow1800, "../outputs/LandscapeCombustion/belowCombustion1800.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(cropBelow1889, "../outputs/LandscapeCombustion/belowCombustion1889.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(cropBelow5938, "../outputs/LandscapeCombustion/belowCombustion5938.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(cropBelow6393, "../outputs/LandscapeCombustion/belowCombustion6393.tif", overwrite=TRUE, filetype="GTiff")
writeRaster(cropBelow8301, "../outputs/LandscapeCombustion/belowCombustion8301.tif", overwrite=TRUE, filetype="GTiff")
```

